Notes of Chapter 2 of Bernevig's Book

### 2017-03-25 Notes of Bernevig's Book/Notes.tex
[minor] Fixed a typo.

\section{Deriving Berry Phase}
\label{sec:Deriving-Berry-Phase}
From page 1 to page 2 (equation 2.7), one derives the expression for
the phase $e^{i\gamma_m}$ using instaneous energy eigenstate for
$E_m$:
\begin{align}
    & H(\vec{R})\ket{n(\vec{R})} = E_m(\vec{R})\ket{n(\vec{R})} \\
    & \gamma_m = i\int_0^t
    \braket{
        m\left(\vec{R}(t')\right)|\frac{\partial }{\partial t}
        m\left(\vec{R}(t')\right) \dd t' }
\end{align}
Then I writes about different ways to get the $\gamma_m$:
\begin{align}
    \gamma_m = i\int_{\text{curve}}\braket{m|\nabla_{\vec{R}}\, m }
    \dd \vec{R}
    = \int_{\text{curve}} \vec{A}_n \vdot\dd \vec{R}
\end{align}
(equation 2.8) 
where one defines
\begin{defi}[Berry Connection, Berry Vector Potential $\vec{A}$]
\nomenclature{Berry Connection, Berry Vector Potential
$\vec{A}$}{\nomrefpage.}
    \begin{align}
        \vec{A}_n \equiv i \braket{n|\nabla_{\vec{R}}\, n }
    \end{align}
\end{defi}
Then I proves several facts:
\begin{fact}
    \label{fact:gamma_is_real}
        $\gamma_n$ is real
\end{fact}
By virtue of fact \ref{fact:gamma_is_real}, we have
\begin{align}
    \gamma_n = -\Im \int_\text{curve} \braket{ n|\nabla_{\vec{R}}\,n}
    \vdot \dd \vec{R} 
\end{align}
\begin{fact}
    Berry connection $\vec{A}_n$ is gauge-dependent.
    The dependence is: If 
    $$\ket{n}\to \ket{n'}= e^{i\xi(\vec{R})}\ket{n}$$
    then
    \begin{align}
        \vec{A}_n \to \vec{A}_n - \nabla_{\vec{R}}\,\xi(\vec{R})
    \end{align}
\end{fact}
Therefore we have
\begin{fact}
    $\gamma_n$ is gauge-dependent, unless the path transverses a
    closed loop.
    Since 
    $$ \gamma_n \to \gamma_n - \left(\xi(\vec{R}(T))-
    \xi(\vec{R}(0)) \right) $$
    It is unchanged unless the integration curve is a closed loop. In
    which case
    $$\xi(\vec{R}(T)) - \xi(\vec{R}(0)) = 2\pi m
    \overset{\text{mod }2\pi}{=} 0 $$
\end{fact}
\begin{ex}
    There is a simple example on page 3 to show that the Berry phase
    can be actually detected.
\end{ex}

When the parameter space is $\mathbb{R}^3$, we have a simpler
expression for berry phase. It is derived on page 4 (equation 2.12)
that
\begin{align}
    \gamma_n = -\Im \oint \braket{\grad_{\vb{R}}
    n|\cross|\grad_{\vb{R}} n} \vdot \dd \vb{s}
    = -\Im \oint \mathcal{A}^n \vdot \dd\vb{s}
\end{align}
where we have defined:
\begin{defi}[Berry Curvature $\mathcal{A}^n$]
\nomenclature{Berry Curvature $\mathcal{A}^n$}{\nomrefpage.}
    \begin{align}
        \mathcal{A}^n = \braket{\grad_{\vb{R}} n|\cross|\grad_{\vb{R}} n}
    \end{align}
    In components (repeated index automatically summed):
    \begin{align}
        \mathcal{A}_i^n = \varepsilon_{ijk} \braket{\partial_j n |
        \partial_k n}
    \end{align}
\end{defi}
By analogy with the theory of electromagnetic fields, this is also
called Berry field, dentoed by $F_{jk}$ in Bernevig's book.
\nomenclature{Berry field $F_{jk}$}{\nomrefpage}. More specifically:
$F_{jk} = \braket{\partial_j n(\vb{R})|\partial_j n(\vb{R})} - (j
    \leftrightarrow k) $.

\section{Gauge-independent calculation of Berry Curvature}
\label{sec:Gauge-independent-calculation-of-Berry-Curvature}
For numerical considerations, we Bernevig gives a new way to calculate
the Berry curvature. I shows in page 5 to 6 that:
\begin{align}
    \gamma_n = -\Im \oint \dd\vb{s} \sum_{m\neq n}
    \frac{\bra{n(\vb{R})}\grad_{\vb{R}} H \ket{m(\vb{R})}
        \cross \bra{m(\vb{R})}\grad_{\vb{R}} H \ket{n(\vb{R})} }
        {(E_n-E_m)^2}
\end{align}
There are two advantages of this formula:
\begin{enumerate}
    \item It is intrinsically gauge-independent (see page 6 for
        explanation).
    \item It is nolonger necessary to pick $\ket{n}$ to be smooth \&
        single-valued. \marginpar{Don't know why}
\end{enumerate}
There are several remarks about this formula on page 7. One important
remark is that:
\begin{fact}
    \begin{align}
        \sum_n \gamma_n = 0
    \end{align}
\end{fact}

\section{Degeneracy and level-crossing}
\label{sec:Degeneracy-and-level-crossing}
Page 7 has a discussion about the serious problems posed by the
degenracy points. Then we turn our attention to two-level system.

    \subsection{Two-level system and Berry connection
    \texorpdfstring{$\vb{A}_n$}{}}
    \label{sec:Two-level-system-and-Berry-connection}
    Here Bernevig considers a system with Hamiltonian
    \begin{equation}
        H = \epsilon(\vb{R}) I + \vb{d}(\vb{R})\vdot\vb{\sigma}
    \end{equation}

    He first calculate in a general setting and concludes that the Berry
    field is
    \begin{equation}
        \vb{V}_{-} = \frac{1}{2}\frac{\vb{d}}{d^3}
    \end{equation}
    However, I don't think it is a good calculation, explained in page 8.
    On the other hand, Bernevig also gives an alternative calculation in
    the following.

        \subsubsection{Two-level system using Hamiltonian approach}
        \label{sec:Two-level-system-using-Hamiltonian-approach}
        On page 8 to 10, I gives the calculation of Berry phase of
        Spin in a varying magnetic environment. Consider the
        Hamiltonian:
        \begin{equation}
            H(\vb{B}) = \vb{B}\vdot \vb{S} 
        \end{equation}
        with
        \begin{equation}
            n = -s, -s+1,\cdots, s
        \end{equation}
        One finds:
        \begin{align}
            \gamma_n = - n\oint \frac{\vb{B}}{B^3} \dd\vb{s}
        \end{align}
        (equation 2.31)
        If the integration is taken on the surface of a sphere, then
        we have (noting that the solid angle $\dd
        \Omega=\sin(\theta)\dd\theta\dd\phi$. Use $\Omega$ to denote
        the solid angle of the integration area)
        \begin{equation}
            e^{i\gamma_n} = e^{-i n \Omega}
        \end{equation}

        There are several remarks on page 10. The important ones are
        \begin{remark}
            If we integrate in a whole sphere, and the sphere contains
            several "poles" - the degeneracy point, we have
            \begin{align}
                |\gamma_i| = 4\pi n \times \text{(number of poles
                inside)}
            \end{align}
            Similary, if the paremeter space in 2 dimensional, then
            \begin{align}
                |\gamma_i| = 2\pi n \times \text{(number of poles
                inside)}
            \end{align}
            Specifically, for electrons
            \begin{align}
                |\gamma_i| = \pi \times \text{(number of poles
                inside)}
            \end{align}
            Therefore, an electron transversing a circle will
            accumulate a phase of $e^{i\pi}=-1$.
        \end{remark}
\section{Anchor}
\label{sec:Anchor}

>>>>

\section{Skipped}

\section{Berry Phase}
\input{sections/chapter2-berry-phase}

\section{Hall Conductance and Chern Numbers}

This chapter is written in an unbelievably hard to read style. I
skipped it almost completely. There are a few hand written notes,
which are not worth even re-read.

\section{Time-Reversal Symmetry}

This chapter contains material important for quantum mechanics in
general and I had written another note bearing the same name for this
chapter. Since that note is too big to be contained here, I will left
here empty and advice one search for "TR Symmetry" in this
repository for that note.

\section{Magnetic Field on the Square Lattice}

\section{Anchor}
\label{sec:Anchor}

### 2017-03-25 Notes of Bernevig's Book/sections/Ch4 TR symmetry/Notes about TR symmetry.tex
[minor] Fixed a typo.

    One can show that \textbf{$T$ must be antilinear}. Because if one
    assumes that $T$ is linear, one will find that the energy
    spectrum for time reversal symmetric system will always has symmetric
    energy spectrum (i.e. with both and symmetric positive and negative
    energy), which is not true.

@@

    Recall that $T= UK$, and $K$ is highly dependent on the basis
    chosen. So $U$ will depend on the basis too. To get $T$ in a
    basis $\ket{e_i}$, obviously we only need to consider the result of
    $K\ket{e_i}$. This however, is hard to determine. However we can argue
    that in case when the basis has some classical connection, then by the
    Correspondance Principle we have, for example:
    \begin{align}
        T \hat{p} T^{-1}&= -\hat{p} \\
        T \hat{x} T^{-1}&= \hat{x} \\
        T \mathbf{J} T^{-1}&= -\mathbf{J}
    \end{align}
    with these one can easily find:
    \begin{align}
        T \ket{p} &= \ket{-p} \\
        T \ket{x} &= \ket{x} \\
        [x_i, p_j]T \ket{} &= i\hbar \delta_{ij} T\ket{}
    \end{align}
    where $\ket{}$ stands for any ket. Then clearly, $T$ is just
    complex conjugation for wave function $\Psi(x)$. But $T$ acts on
    $\Psi(p)$ will produces $\Psi^*(-p)$. The case for eigenstate of
    spin is a little complicated, which will be discussed in section
    \ref{sec:Time-reversal-operator-in-spin-j}.

@@

    However, if we imagine a spin $j$ system as composed all just of
    electrons of spin $\frac{1}{2}$, then we have a strong argument that
    the above formula is true.
    \subsection{Kramer's theorem and the lifting of degenracy}
    \label{sec:Kramers-theorem-and-the-lifting-of-degenracy}
    When one is concerned with the energy spectrum, one encounters the
    Kramer's theorem, which says:
    \begin{thm}[Kramer's theorem]
        For a system with halt-integer $j$ spin, the degree of degeneracy
        is at least two.
    \end{thm}
    \begin{proof}
        Let $\ket{n}$ be an energy eigenstate. If the system is time
        reversal symmetric, i.e. $[H,T]=0$, then $T \ket{n}$ is
        another energy eigenstate with the same energy. Supposing there is
        no degeneracy, then we have
        $$ \ket{n} = e^{i\eta}T\ket{n}$$
        for some $\eta\in \mathbb{R}$. Apply $T$ on both sides, then
        we have
        \begin{align*}
            e^{-i\eta} T^2 \ket{n} &= \pm e^{-i\eta}\ket{n} \\
            &= T \ket{n} = e^{i\eta} \ket{n}
        \end{align*}
        Clearly this is a contracdiction unless $T^2=1$, which is
        true only for interger spin system by equation
        \ref{eq:TRoper.TRoper.square_plus} and
        \ref{eq:TRoper.TRoper.square_minus}.
    \end{proof}
    Another way to show this is presented in page 37 of
    \cite{bernevig}. That method is too troublesome and basis dependent 
    \footnote{Borrowing the jargon of mathematicians, not canonical,
        geometric, or intrinsic.}
    to be shown here.
    But it shows an interesting fact that $T^2=-1$, actually
    implies that $U$, its unitary component mentioned in section
    \ref{sec:Property-of-symmetry-operator}, is antisymmetric. This is
    obvious when one juxtapose the following two facts:
    $$ U (U^*)^T = \mathbbm{1}$$
    $$ T^2 = UKUK = U U^* = -\mathbbm{1} $$

>>>>

    One can show that \textbf{$T$ must be antilinear}. Because if one
    assumes that $T$ is linear, one will find that the energy
    spectrum for time reversal symmetric system will always has symmetric
    energy spectrum (i.e. with both positive and negative
    energy), which is not true.

@@

    Recall that $T= UK$, and $K$ is highly dependent on the basis
    chosen. So $U$ will depend on the basis too. To get $T$ in a
    basis $\ket{e_i}$, obviously we only need to consider the result of
    $U\ket{e_i}$. This however, is hard to determine. However we can argue
    that in case when the basis has some classical connection, then by the
    Correspondance Principle we have, for example:
    \begin{align}
        T \hat{p} T^{-1}&= -\hat{p} \\
        T \hat{x} T^{-1}&= \hat{x} \\
        T \mathbf{J} T^{-1}&= -\mathbf{J}
    \end{align}
    with these one can easily find:
    \begin{align}
        T \ket{p} &= \ket{-p} \\
        T \ket{x} &= \ket{x} \\
        [x_i, p_j]T \ket{} &= i\hbar \delta_{ij} T\ket{}
    \end{align}
    where $\ket{}$ stands for any ket. Then clearly, $T$ is just
    complex conjugation for wave function $\Psi(x)$. But $T$ acts on
    $\Psi(p)$ will produces $\Psi^*(-p)$. The case for eigenstate of
    spin is a little complicated, which will be discussed in section
    \ref{sec:Time-reversal-operator-in-spin-j}.

@@

    However, if we imagine a spin $j$ system as composed all just of
    electrons of spin $\frac{1}{2}$, then we have a strong argument that
    the above formula is true.
    \subsection{Kramer's theorem and the lifting of degenracy}
    \label{sec:Kramers-theorem-and-the-lifting-of-degenracy}
    When one is concerned with the energy spectrum, one encounters the
    Kramer's theorem, which says:
    \begin{thm}[Kramer's theorem]
        For a system with halt-integer $j$ spin, the degree of degeneracy
        is at least two.
    \end{thm}
    \begin{proof}
        Let $\ket{n}$ be an energy eigenstate. If the system is time
        reversal symmetric, i.e. $[H,T]=0$, then $T \ket{n}$ is
        another energy eigenstate with the same energy. Supposing there is
        no degeneracy, then we have
        $$ \ket{n} = e^{i\eta}T\ket{n}$$
        for some $\eta\in \mathbb{R}$. Apply $T$ on both sides, then
        we have
        \begin{align*}
            e^{-i\eta} T^2 \ket{n} &= \pm e^{-i\eta}\ket{n} \\
            &= T \ket{n} = e^{-i\eta} \ket{n}
        \end{align*}
        Clearly this is a contracdiction unless $T^2=1$, which is
        true only for interger spin system by equation
        \ref{eq:TRoper.TRoper.square_plus} and
        \ref{eq:TRoper.TRoper.square_minus}.
    \end{proof}
    Another way to show this is presented in page 37 of
    \cite{bernevig}. That method is too troublesome and basis dependent 
    \footnote{Borrowing the jargon of mathematicians, not canonical,
        geometric, or intrinsic.}
    to be shown here.
    But it shows an interesting fact that $T^2=-1$, actually
    implies that $U$, its unitary component mentioned in section
    \ref{sec:Property-of-symmetry-operator}, is antisymmetric. This is
    obvious when one juxtapose the following two facts:
    $$ U (U^*)^T = \mathbbm{1}$$
    $$ T^2 = UKUK = U U^* = -\mathbbm{1} $$

### 2017-03-25 Notes of Bernevig's Book/sections/chapter2-berry-phase.tex
[minor] Fixed a typo.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{bbm} % for numbers within mathbb
\usepackage{mathrsfs} % For \mathscr{ABC}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref

% For highlighting
\usepackage{color,soul}

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\newtheorem{fact}{Fact}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]
\newtheorem{argument}{Argument}[section]

% A list of nomenclatures.
\usepackage{nomencl}
\makenomenclature

% For drawing diagrams with arrows
\usepackage[all]{xy}

% -=---------------- My Own New commands ---------------
\usepackage[log-declarations=false]{xparse}
\usepackage{physics-taper}
% Referenced package: \usepackage{physics}

%  Vector notation ---------------------
% \DeclareDocumentCommand\vectorbold{ s m }{
%     \IfBooleanTF{#1}
%     {\boldsymbol{#2}}
%     {\mathbf{#2}}
% } % Vector bold [star for Greek and italic Roman]
% \DeclareDocumentCommand\vb{}{\vectorbold} % Shorthand for \vectorbold
% 
% \DeclareDocumentCommand\vectorunit{ s m }{
%     \IfBooleanTF{#1}
%     {\boldsymbol{\hat{#2}}}
%     {\mathbf{\hat{#2}}}
% } % Unit vector [star for Greek and italic Roman]
% \DeclareDocumentCommand\vu{}{\vectorunit} % Shorthand for \vectorunit
% 
% \DeclareDocumentCommand\vdot{}{\boldsymbol\cdot} % Vector dot product symbol
% \DeclareDocumentCommand\cross{}{\boldsymbol\times} % Vector cross product symbol
% \DeclareDocumentCommand\vnabla{}{\boldsymbol\nabla} % Vector bold \nabla symbol
% \DeclareDocumentCommand\grad{}{\vnabla} 
% \DeclareDocumentCommand\dive{}{\vnabla\vdot} 
% \DeclareDocumentCommand\curl{}{\vnabla\cross}
% \DeclareDocumentCommand\laplacian{}{\nabla^2} 
% 
% % Operators ----------------------------
% \let\imaginary\Im
% \RenewDocumentCommand\Im{g}{
%     \IfNoValueTF{#1}
%     {\operatorname{Im}}
%     {\operatorname{Im}\left\{ #1 \right\}}
% }
% \let\real\Re
% \DeclareDocumentCommand\Re{g}{
%     \IfNoValueTF{#1}
%     {\operatorname{Re}}
%     {\operatorname{Re} \left\{ #1 \right\} }
% }
\title{Notes of Chapter 2 of Bernevig's Book}
\date{\today}
\author{Taper}

\begin{document}

\maketitle
\abstract{
Since I have already made a written one, this note is only an outline
of the written script, in the hope of makeing it eaiser to read.
}
\tableofcontents

\section{Deriving Berry Phase}
\label{sec:Deriving-Berry-Phase}
From page 1 to page 2 (equation 2.7), one derives the expression for
the phase $e^{i\gamma_m}$ using instaneous energy eigenstate for
$E_m$:
\begin{align}
    & H(\vec{R})\ket{n(\vec{R})} = E_m(\vec{R})\ket{n(\vec{R})} \\
    & \gamma_m = i\int_0^t
    \braket{
        m\left(\vec{R}(t')\right)|\frac{\partial }{\partial t}
        m\left(\vec{R}(t')\right) \dd t' }
\end{align}
Then I writes about different ways to get the $\gamma_m$:
\begin{align}
    \gamma_m = i\int_{\text{curve}}\braket{m|\nabla_{\vec{R}}\, m }
    \dd \vec{R}
    = \int_{\text{curve}} \vec{A}_n \vdot\dd \vec{R}
\end{align}
(equation 2.8) 
where one defines
\begin{defi}[Berry Connection, Berry Vector Potential $\vec{A}$]
\nomenclature{Berry Connection, Berry Vector Potential
$\vec{A}$}{\nomrefpage.}
    \begin{align}
        \vec{A}_n \equiv i \braket{n|\nabla_{\vec{R}}\, n }
    \end{align}
\end{defi}
Then I proves several facts:
\begin{fact}
    \label{fact:gamma_is_real}
        $\gamma_n$ is real
\end{fact}
By virtue of fact \ref{fact:gamma_is_real}, we have
\begin{align}
    \gamma_n = -\Im \int_\text{curve} \braket{ n|\nabla_{\vec{R}}\,n}
    \vdot \dd \vec{R} 
\end{align}
\begin{fact}
    Berry connection $\vec{A}_n$ is gauge-dependent.
    The dependence is: If 
    $$\ket{n}\to \ket{n'}= e^{i\xi(\vec{R})}\ket{n}$$
    then
    \begin{align}
        \vec{A}_n \to \vec{A}_n - \nabla_{\vec{R}}\,\xi(\vec{R})
    \end{align}
\end{fact}
Therefore we have
\begin{fact}
    $\gamma_n$ is gauge-dependent, unless the path transverses a
    closed loop.
    Since 
    $$ \gamma_n \to \gamma_n - \left(\xi(\vec{R}(T))-
    \xi(\vec{R}(0)) \right) $$
    It is unchanged unless the integration curve is a closed loop. In
    which case
    $$\xi(\vec{R}(T)) - \xi(\vec{R}(0)) = 2\pi m
    \overset{\text{mod }2\pi}{=} 0 $$
\end{fact}
\begin{ex}
    There is a simple example on page 3 to show that the Berry phase
    can be actually detected.
\end{ex}

@@

\section{Gauge-independent calculation of Berry Curvature}
\label{sec:Gauge-independent-calculation-of-Berry-Curvature}
For numerical considerations, we Bernevig gives a new way to calculate
the Berry curvature. I shows in page 5 to 6 that:
\begin{align}
    \gamma_n = -\Im \oint \dd\vb{s} \sum_{m\neq n}
    \frac{\bra{n(\vb{R})}\grad_{\vb{R}} H \ket{m(\vb{R})}
        \cross \bra{m(\vb{R})}\grad_{\vb{R}} H \ket{n(\vb{R})} }
        {(E_n-E_m)^2}
\end{align}
There are two advantages of this formula:
\begin{enumerate}
    \item It is intrinsically gauge-independent (see page 6 for
        explanation).
    \item It is nolonger necessary to pick $\ket{n}$ to be smooth \&
        single-valued. \marginpar{Don't know why}
\end{enumerate}
There are several remarks about this formula on page 7. One important
remark is that:
\begin{fact}
    \begin{align}
        \sum_n \gamma_n = 0
    \end{align}
\end{fact}

\section{Degeneracy and level-crossing}
\label{sec:Degeneracy-and-level-crossing}
Page 7 has a discussion about the serious problems posed by the
degenracy points. Then we turn our attention to two-level system.

    \subsection{Two-level system and Berry connection
    \texorpdfstring{$\vb{A}_n$}{}}
    \label{sec:Two-level-system-and-Berry-connection}
    Here Bernevig considers a system with Hamiltonian
    \begin{equation}
        H = \epsilon(\vb{R}) I + \vb{d}(\vb{R})\vdot\vb{\sigma}
    \end{equation}

@@

        \subsubsection{Two-level system using Hamiltonian approach}
        \label{sec:Two-level-system-using-Hamiltonian-approach}
        On page 8 to 10, I gives the calculation of Berry phase of
        Spin in a varying magnetic environment. Consider the
        Hamiltonian:
        \begin{equation}
            H(\vb{B}) = \vb{B}\vdot \vb{S} 
        \end{equation}
        with
        \begin{equation}
            n = -s, -s+1,\cdots, s
        \end{equation}
        One finds:
        \begin{align}
            \gamma_n = - n\oint \frac{\vb{B}}{B^3} \dd\vb{s}
        \end{align}
        (equation 2.31)
        If the integration is taken on the surface of a sphere, then
        we have (noting that the solid angle $\dd
        \Omega=\sin(\theta)\dd\theta\dd\phi$. Use $\Omega$ to denote
        the solid angle of the integration area)
        \begin{equation}
            e^{i\gamma_n} = e^{-i n \Omega}
        \end{equation}

        There are several remarks on page 10. The important ones are
        \begin{remark}
            If we integrate in a whole sphere, and the sphere contains
            several "poles" - the degeneracy point, we have
            \begin{align}
                |\gamma_i| = 4\pi n \times \text{(number of poles
                inside)}
            \end{align}
            Similary, if the paremeter space in 2 dimensional, then
            \begin{align}
                |\gamma_i| = 2\pi n \times \text{(number of poles
                inside)}
            \end{align}
            Specifically, for electrons
            \begin{align}
                |\gamma_i| = \pi \times \text{(number of poles
                inside)}
            \end{align}
            Therefore, an electron transversing a circle will
            accumulate a phase of $e^{i\pi}=-1$.
        \end{remark}
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
    \bibitem{book} Bernevig's Topological Insulators and
    Superconductors
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\subsection{Deriving Berry Phase}
\label{sec:Deriving-Berry-Phase}
From page 1 to page 2 (equation 2.7), one derives the expression for
the phase $e^{i\gamma_m}$ using instaneous energy eigenstate for
$E_m$:
\begin{align}
    & H(\vec{R})\ket{n(\vec{R})} = E_m(\vec{R})\ket{n(\vec{R})} \\
    & \gamma_m = i\int_0^t
    \braket{
        m\left(\vec{R}(t')\right)|\frac{\partial }{\partial t}
        m\left(\vec{R}(t')\right) \dd t' }
\end{align}
Then I writes about different ways to get the $\gamma_m$:
\begin{align}
    \gamma_m = i\int_{\text{curve}}\braket{m|\nabla_{\vec{R}}\, m }
    \dd \vec{R}
    = \int_{\text{curve}} \vec{A}_n \vdot\dd \vec{R}
\end{align}
(equation 2.8) 
where one defines
\begin{defi}[Berry Connection, Berry Vector Potential $\vec{A}$]
\nomenclature{Berry Connection, Berry Vector Potential
$\vec{A}$}{\nomrefpage.}
    \begin{align}
        \vec{A}_n \equiv i \braket{n|\nabla_{\vec{R}}\, n }
    \end{align}
\end{defi}
Then I proves several facts:
\begin{fact}
    \label{fact:gamma_is_real}
        $\gamma_n$ is real
\end{fact}
By virtue of fact \ref{fact:gamma_is_real}, we have
\begin{align}
    \gamma_n = -\Im \int_\text{curve} \braket{ n|\nabla_{\vec{R}}\,n}
    \vdot \dd \vec{R} 
\end{align}
\begin{fact}
    Berry connection $\vec{A}_n$ is gauge-dependent.
    The dependence is: If 
    $$\ket{n}\to \ket{n'}= e^{i\xi(\vec{R})}\ket{n}$$
    then
    \begin{align}
        \vec{A}_n \to \vec{A}_n - \nabla_{\vec{R}}\,\xi(\vec{R})
    \end{align}
\end{fact}
Therefore we have
\begin{fact}
    $\gamma_n$ is gauge-dependent, unless the path transverses a
    closed loop.
    Since 
    $$ \gamma_n \to \gamma_n - \left(\xi(\vec{R}(T))-
    \xi(\vec{R}(0)) \right) $$
    It is unchanged unless the integration curve is a closed loop. In
    which case
    $$\xi(\vec{R}(T)) - \xi(\vec{R}(0)) = 2\pi m
    \overset{\text{mod }2\pi}{=} 0 $$
\end{fact}
\begin{ex}
    There is a simple example on page 3 to show that the Berry phase
    can be actually detected.
\end{ex}

@@

\subsection{Gauge-independent calculation of Berry Curvature}
\label{sec:Gauge-independent-calculation-of-Berry-Curvature}
For numerical considerations, we Bernevig gives a new way to calculate
the Berry curvature. I shows in page 5 to 6 that:
\begin{align}
    \gamma_n = -\Im \oint \dd\vb{s} \sum_{m\neq n}
    \frac{\bra{n(\vb{R})}\grad_{\vb{R}} H \ket{m(\vb{R})}
        \cross \bra{m(\vb{R})}\grad_{\vb{R}} H \ket{n(\vb{R})} }
        {(E_n-E_m)^2}
\end{align}
There are two advantages of this formula:
\begin{enumerate}
    \item It is intrinsically gauge-independent (see page 6 for
        explanation).
    \item It is nolonger necessary to pick $\ket{n}$ to be smooth \&
        single-valued. \marginpar{Don't know why}
\end{enumerate}
There are several remarks about this formula on page 7. One important
remark is that:
\begin{fact}
    \begin{align}
        \sum_n \gamma_n = 0
    \end{align}
\end{fact}

\subsection{Degeneracy and level-crossing}
\label{sec:Degeneracy-and-level-crossing}
Page 7 has a discussion about the serious problems posed by the
degenracy points. Then we turn our attention to two-level system.

    \subsubsection{Two-level system and Berry connection
    \texorpdfstring{$\vb{A}_n$}{}}
    \label{sec:Two-level-system-and-Berry-connection}
    Here Bernevig considers a system with Hamiltonian
    \begin{equation}
        H = \epsilon(\vb{R}) I + \vb{d}(\vb{R})\vdot\vb{\sigma}
    \end{equation}

@@

        \paragraph{Two-level system using Hamiltonian approach}
        \label{sec:Two-level-system-using-Hamiltonian-approach}
        On page 8 to 10, I gives the calculation of Berry phase of
        Spin in a varying magnetic environment. Consider the
        Hamiltonian:
        \begin{equation}
            H(\vb{B}) = \vb{B}\vdot \vb{S} 
        \end{equation}
        with
        \begin{equation}
            n = -s, -s+1,\cdots, s
        \end{equation}
        One finds:
        \begin{align}
            \gamma_n = - n\oint \frac{\vb{B}}{B^3} \dd\vb{s}
        \end{align}
        (equation 2.31)
        If the integration is taken on the surface of a sphere, then
        we have (noting that the solid angle $\dd
        \Omega=\sin(\theta)\dd\theta\dd\phi$. Use $\Omega$ to denote
        the solid angle of the integration area)
        \begin{equation}
            e^{i\gamma_n} = e^{-i n \Omega}
        \end{equation}

        There are several remarks on page 10. The important ones are
        \begin{remark}
            If we integrate in a whole sphere, and the sphere contains
            several "poles" - the degeneracy point, we have
            \begin{align}
                |\gamma_i| = 4\pi n \times \text{(number of poles
                inside)}
            \end{align}
            Similary, if the paremeter space in 2 dimensional, then
            \begin{align}
                |\gamma_i| = 2\pi n \times \text{(number of poles
                inside)}
            \end{align}
            Specifically, for electrons
            \begin{align}
                |\gamma_i| = \pi \times \text{(number of poles
                inside)}
            \end{align}
            Therefore, an electron transversing a circle will
            accumulate a phase of $e^{i\pi}=-1$.
        \end{remark}
